\clearpage
\phantomsection
\addcontentsline{toc}{section}{\refname}


\begin{thebibliography}{99}

\bibitem{Curie:Monopole}
M. P. Curie,
\emph{Sur la possibilité d'existence de la conductibilité magnétique et du magnétisme libre},
Seances de la Societé Francaise de Physique (Paris), p.\ 76 (1894), 
\url{http://www.archive.org/stream/sancesdelasocit19physgoog#page/n82/mode/2up}

\bibitem{Dirac}
P. A. M. Dirac,
\emph{Quantised singularities in the electromagnetic field}, Proc. R. Soc. A133 (1931), 60-72.

\bibitem{Hof:Mon}
G. 't Hooft, \emph{Magnetic monopoles in unified gauge theories}, Nuc.Phys. B79 (1974), 276-284.

\bibitem{Pol:Mon}
A. M. Polyakov, \emph{Particle spectrum in quantum Field theory}, JETP Letters 20 (1974), 194-195.

\bibitem{Julia:Dyon}
B. Julia and A. Zee, \emph{Poles with both magnetic and electric charges
in non-abelian gauge theories}, Phys. Rev. D11 (1975), 2227-2232.

\bibitem{S:dyon}
J. S. Schwinger, \emph{Magnetic charge and quantum field theory}, Phys. Rev. 144 1087, (1966).

\bibitem{Z:dyon}
Daniel Zwanziger,\emph{Quantum Field Theory of Particles with Both Electric and Magnetic Charges} Phys. Rev. 176, 1489 (1968).

\bibitem{Fig:EDC}
Figueroa J.M. O'Farrill, \emph{Electromagnetic Duality for Children}, ntcatlab.org
(1998).

\bibitem{Taubes:Sol}
C. H. Taubes, \emph{Stability in Yang Mills theories}, Comm. Math.
Phys. 91 (1983), 473-540.

\bibitem{Bogomolny}
E. B. Bogomolny, \emph{Stability of Classical Solutions}, Sov. J. Nucl. Phys. 24 (1976), 449; Yad. Fiz. 24 (1976), 861.

\bibitem{PrasSom}
 Prasad, M. K.; Sommerfield, Charles M., \emph{An Exact Classical Solution for the 't Hooft Monopole and the Julia-Zee Dyon}, Physical Review Letters (22 September 1975), American Physical Society.

\bibitem{Lechner}
K. Lechner, \emph{Elettrodinamica classica}, Springer 2014







\end{thebibliography}